---
title: "Empirically fitting the spike data"
output: html_document
---

Read in the data.

```{r}
library(R.matlab)
dat <- readMat('/home/snarles/stat312data/spike_dat.mat')
trial <- dat$trial
dim(trial)
length(as.vector(trial[2, 1 ,1]$spikes)) # 500
angles <- c(30, 70, 110, 150, 190, 230, 310, 350)/180 * pi
temp <- trial[2, , ]
spikes <- array(0, c(8, 182, 500))
for (i in 1:8) {
  for (j in 1:182) {
    spikes[i, j, ] = as.vector(trial[2, j, i]$spikes)
  }
}
```

Mean rates for each angle
```{r, fig.width=6, fig.height=3}
meanrates <- apply(spikes, 1, mean)
plot(angles, meanrates, type='l', ylab = "spikes per ms", xlab = "reaching angle (radians)")
for (k in 1:8) {
  text(angles[k], meanrates[k], paste(k))
}
title("Mean firing rate by k")
```

Choose k = 6, get ISIs

```{r}
x <- spikes[6, , ]
temp <- apply(x, 1, function(v) which(v==1))
temp <- lapply(temp, function(v) v[-1]-v[-length(v)] )
isi_s <- unlist(temp)
```

Histogram vs exponential fit
```{r, fig.width=5, fig.height=3}
max(isi_s)
breaks <- seq(0, 310, 10)
hist(isi_s, breaks = breaks)
rate_hat <- 1/mean(isi_s)
scaling <- length(isi_s) * 10
est <- dexp(breaks, rate_hat)
lines(breaks, scaling * dexp(breaks, rate_hat))
```

Supposing we bin by 5 ms, how many repeats will we get?

```{r}
binwidth <- 5
binmat <- diag(rep(1, 500/binwidth)) %x% matrix(1, binwidth, 1)
dim(binmat)
binned <- x %*% binmat
table(as.vector(binned))
```

Coerce the 2s to 1s and fit the autoregressive logistic model

```{r, fig.width=5, fig.height=3}
library(glmnet)
binned[binned > 1] <- 1
ord <- 20 # order of the autoregressive model by bins
create_ar_matrix <- function(x, order) {
  n <- length(x) - order
  ans <- matrix(0, n, order)
  for (i in 1:n) {
    ans[i, ] <- rev(x[i:(i+order - 1)])
  }
  ans
}
expanded <- numeric(0)
for (i in 1:dim(binned)[1]) {
  expanded <- rbind(expanded, create_ar_matrix(binned[i, ], ord))
}
dim(expanded)
res <- glm(expanded[, 1] ~ expanded[, -1], family = binomial)
coeffs <- coef(res)
plot(coef(res)[-1], type="o")
abline(0, 0)
title("Logistic autoregression")
```

The empirical proportion
```{r}
sum(expanded[,1])/length(expanded[,1])
```

Simulate a sequence starting from zeros
```{r, fig.width=5, fig.height=3}
seq <- rep(0, ord)
nseq <- 100000
for (i in 1:nseq) {
  prev <- rev(seq[(length(seq)-ord+2):length(seq)])
  temp <- coeffs[1] + sum(coeffs[-1] * prev)
  prob <- exp(temp)/(1+exp(temp))
  new_y <- rbinom(1, 1, prob)
  seq <- c(seq, new_y)
}
plot(seq[500:1000], type="l")
title("spikes")
```

Check the simulatied proportion
```{r}
sum(seq[500:nseq])/length(500:nseq)
```

Compute the ISIs of the simulated spikes (minus a burn-in)
```{r, fig.width=5, fig.height=3}
temp <- which(seq[500:nseq]==1)
sim_isi_s <- binwidth * (temp[-1] - temp[-length(temp)])
hist(sim_isi_s, 20)
```

We have a censoring issue, since empirical ISIs are limited by the size of the interval (500ms)
Therefore we need to chunk the simulated ISIs into bins of size 500 and take the distribution that would be observed.

```{r}
stimes <- cumsum(sim_isi_s)
intervals <- floor(stimes / 500)
sim_observed_isi_s <- (stimes[-1] - stimes[-length(stimes)])[intervals[-1] == intervals[-length(stimes)]]
hist(sim_observed_isi_s)
```

Now compare the plots

```{r, fig.width=5, fig.height=5}
length(isi_s)
plot(quantile(sim_observed_isi_s, 1:length(isi_s)/length(isi_s)), sort(isi_s))
abline(0, 1)
```

