Exercise 4
========================================================
Nora Brackbill and Charles Zheng

## Model

FDR

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

## Load the data

```{r, cache=FALSE}
library('car')
library('pdist')
load('ex4.RData')
```

## Visualize the filters

```{r fig.width=5, fig.height=6}
rematwav <- function(ind, wav = wav.pyr) {
  wav <- matrix(Re(wav[, ind]), 128, 128)
}
old.par <- par()
layout(matrix(1:42, 7, 6))
par(mar = c(0,0,0,0))
for (i in which(vertical_features)) {
  image(rematwav(i, wav.pyr42))  
}
for (i in which(horizontal_features)) {
  image(rematwav(i, wav.pyr42))  
}
par(old.par)
```

## Get the p-values

```{r}
contrast_vec <- c(0, -1 * vertical_features + 
                   1 * horizontal_features)
nvoxels <- dim(train_resp)[2]
pvs <- numeric(nvoxels)
for (vox in 1:nvoxels) {
  res <- lm(train_resp[, vox] ~ X)
  res2 <- linearHypothesis(res, t(contrast_vec))
  pvs[vox] <- res2$'Pr(>F)'[2]
}
```

How many are significant at level 0.1?

```{r}
sum(pvs < .1)
```

## Plot the p-values

```{r fig.width=7, fig.height=6}
coords <- vl[pvs < .1, ]
plot(vl[,1], vl[,2], col='grey')
points(coords[,1], coords[,2], col='red')
```

Is there clustering? Compare to completely random.

```{r fig.width=7, fig.height=6}
lala <- vl[runif(nvoxels) < .1, ]
plot(vl[,1], vl[,2], col='grey')
points(lala[,1], lala[,2], col='red')
```

## Exploring the local correlation structure

Plot nearest-neighbor pairs

```{r fig.width=5, fig.height=6}
dm <- as.matrix(pdist(vl, vl))
pairsX <- row(dm)[dm ==1]
pairsY <- col(dm)[dm ==1]
filt <- pairsX < pairsY
pairsX <- pairsX[filt]
pairsY <- pairsY[filt]
plot(pvs[pairsX], pvs[pairsY], col=rgb(0,0,0, alpha = .5))
```

Log plot

```{r fig.width=5, fig.height=6}
plot(log(pvs[pairsX]), log(pvs[pairsY]), col=rgb(0,0,0, alpha = .5))
```

## Bonferroni correction

How many are significant at FWER = 0.3?

```{r}
sig_voxels <- pvs < .3/nvoxels
sum(sig_voxels)
```

Plot:

```{r fig.width=7, fig.height=6}
coords <- vl[sig_voxels, ]
plot(vl[,1], vl[,2], col='grey')
points(coords[,1], coords[,2], col='red')
```

## BH procedure

Plot of BH estimated FDP
```{r fig.width=5, fig.height=6}
sorted_pvs <- sort(pvs)
fdps <- sorted_pvs * nvoxels/(1:nvoxels)
plot(log(sorted_pvs), fdps)
```

Get the p-value threshold for FDR = 0.3
```{r}
pthres <- max(sorted_pvs[fdps < 0.3])
pthres
```

How many are rejected?
```{r}
fdr_vox <- pvs <= pthres
sum(fdr_vox)
```

Plot:

```{r fig.width=7, fig.height=6}
coords <- vl[fdr_vox, ]
plot(vl[,1], vl[,2], col='grey')
points(coords[,1], coords[,2], col='red')
```
