Exercise 6
========================================================
Nora Brackbill and Charles Zheng

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

## Load the data

```{r, cache=FALSE}
source("gauss_class.R")
source("knn_class.R")
library("R.matlab")
library('mvtnorm')
dat = readMat('ps3_realdata.mat')
```

```{r}
neur = 97
train_trials = 728
test_trials = 728
nlab = 8

vecs = matrix(nr =length(dat$train.trial)/2, nc = neur) 
for (i in seq(2,length(dat$train.trial),2)){
  vecs[i/2,] = rowSums(dat$train.trial[i][[1]][,351:550])
  }
labels = rep(1:8, each = 91) 
nlab = 8
# testing data
test_vecs = matrix(nr =length(dat$test.trial)/2, nc = neur) 
for (i in seq(2,length(dat$test.trial),2)){
  test_vecs[i/2,] = rowSums(dat$test.trial[i][[1]][,351:550]) 
}
```



### Shared Covariance

```{r}
shared_fit = gauss_fit(vecs, nlab, shared = TRUE)

# check the training data
Gauss_SharedCov_Train_Error = sum(gauss_predict(vecs, shared_fit) != labels)/train_trials

# try it out on test data
Gauss_SharedCov_assigned_label = gauss_predict(test_vecs, shared_fit)
Gauss_SharedCov_Test_Error = sum(Gauss_SharedCov_assigned_label != labels)/test_trials
Gauss_SharedCov_Test_Error
```

Look at confusion matrix
```{r}
Gauss_SharedCov_assigned_label[1:20 * 10]
pred_labels <- as.factor(Gauss_SharedCov_assigned_label)
cm <- table(labels, pred_labels)
cm
```

```{r fig.width=5, fig.height=6}
library(corrplot)
corrplot(cm, is.corr=FALSE)
```


### Separate Covariance

INCOMPLETE -- NEED TO REGULARIZE THE COVARIANCE ESTIMATE

```{r}
# estimate the params
shared_fit = gauss_fit(vecs, nlab, shared = FALSE)

# check the training data
Gauss_SeparateCov_Train_Error = sum(gauss_predict(vecs, shared_fit) != labels)/train_trials

# try it out on test data
Gauss_SeparateCov_assigned_label = gauss_predict(test_vecs, shared_fit)
Gauss_SeparateCov_Test_Error = sum(Gauss_SharedCov_assigned_label != labels)/test_trials
Gauss_SeparateCov_Test_Error
```

## K-nearest neighbor
```{r}
library(class)
```

Choose the number of neighbors k.
```{r fig.width=5, fig.height=6}
results <- numeric(30)
for (i in 1:30) {
  res <- knn.cv(vecs, cl=labels, k=i)
  results[i] <- sum(res != labels)
}
plot(results, type = 'b')
```

Set
```{r}
k = 11
```

Use KNN on test set
```{r}
pred_labels <- knn(vecs, test_vecs, labels, k = k)
misc_rate <- sum(pred_labels != labels)/length(labels)
misc_rate
```

Look at confusion matrix
```{r}
cm <- table(labels, pred_labels)
cm
```

```{r fig.width=5, fig.height=6}
library(corrplot)
corrplot2 <- function(x, ...) {
  old.par <- par(no.readonly = TRUE)
  corrplot(x, ...)
  par(old.par)
}
corrplot2(cm, is.corr=FALSE)
```

## Hierarchical Clustering of means

Hierachical clustering of all training points!

```{r fig.width=5, fig.height=6}
tr_dist <- dist(vecs)
res_h <- hclust(tr_dist)
names(res_h)
plot(res_h)

cols <- rainbow(8)
for (i in 1:8) {
  xs <- which(labels[res_h$order] == i)
  ys <- rep(min(res_h$height), length(xs))
  points(xs, ys, pch = '*', col=cols[i])
}
```

Just cluster the means.

```{r fig.width=5, fig.height=6}


shared_fit = gauss_fit(vecs, nlab, shared = TRUE)

isqrtm <- function(m) {
  res <- eigen(m)
  d <- res$values
  d[d < 0] <- 0
  d[d > 0] <- 1/sqrt(d[d > 0])
  v <- res$vectors
  return (v %*% diag(d) %*% t(v))
}

dim(shared_fit$mean)
#mu_dist <- dist(shared_fit$mean)
mu_dist <- dist(shared_fit$mean %*% isqrtm(shared_fit$cov))
res_h <- hclust(mu_dist)
plot(res_h)
```


## Kmeans

```{r fig.width=5, fig.height=6}
max_K <- 30
results <- list(max_K)
for (i in 1:max_K) {
  results[[i]] <- kmeans(vecs, centers = i)
}
plot(sapply(results, function(v) v$tot.withinss))
```

Look at within SS vs number of clusters.

Choose k = 8 to see how well we recover the original clusters.

```{r}
K <- 8
res <- results[[K]]
countmat <- matrix(0, 8, K)
for (i in 1:8) {
  countmat[i, ] <- table(c(1:8, res$cluster[labels == i]))-1
}
```

Match clusters and groups.

```{r}
best_trace <- 0
best_perm <- NULL
for (i in 1:10000) {
  perm <- sample(8, 8, FALSE)
  trr <- sum(diag(countmat[, perm]))
  if (trr > best_trace) {
    best_trace <- trr
    best_perm <- perm
  }
}
```

The confusion matrix.

```{r fig.width=5, fig.height=6}
corrplot2(countmat[, best_perm], is.corr=FALSE)
```

## The distance matrix

Take the SVD of the distance matrix

```{r}
dmat <- as.matrix(tr_dist)
res <- svd(dmat)
```

Look at the singular values

```{r fig.width=5, fig.height=6}
plot(res$d[1:10])
```

Plot the first two directions
```{r fig.width=5, fig.height=6}
plot(res$u[, 1], res$u[, 2], col = rainbow(8)[labels])
```

Plot the second and third directions
```{r fig.width=5, fig.height=6}
plot(res$u[, 2], res$u[, 3], col = rainbow(8)[labels])
```

## Neuron vs Trial

```{r fig.width=5, fig.height=6}
heatmap(vecs, Rowv = NA)
```