Exercise 3
========================================================
Nora Brackbill and Charles Zheng

## Model

We used the lasso objective function $||y - X\beta||^2 + \lambda ||\beta||_1$ to fit a linear model of the features. In a previous analysis, we tried both lasso and ridge, and found that lasso worked slightly better. We also determined that we were best able to model voxel 2.

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

## Load the data

```{r, cache=FALSE}
setwd("Ex3")
for (f in list.files()) {
  if (substring(f,nchar(f)-4, nchar(f))=="RData") {
    load(f)
  }
}
setwd("..")
n_train = 1750
n_valid = 120
n_voxel = 15
n_basis = 10921
library("glmnet")
```

## Fit the model

```{r}
voxel <- 2
res <- cv.glmnet(x = feature_train, y = train_resp[,voxel], alpha = 1, type.measure="mse")
```

What is the best regularization parameter to use?

```{r fig.width=5, fig.height=6}
plot(res)
```

What do the coefficients of the model look like at that lambda?

```{r fig.width=5, fig.height=6}
l <- res$lambda.min
beta_vec <- coef(res, s = l)
plot(beta_vec)
```

What does the corresponding filter look like?
```{r fig.width=5, fig.height=6}
get_filter <- function(beta_vec) {
  inds <- which(beta_vec[-1] > 0)
  cplx <- cos(2*pi*runif(length(inds))) + sin(2*pi*runif(length(inds)))
  filter <- t(cplx * t(wav.pyr[, inds])) %*% beta_vec[inds]
  filter <- matrix(filter, nrow=128, byrow=FALSE)
  return (Re(filter))
}
image(get_filter(beta_vec))
```


Let's see if the result is stable given subsampling our data.

```{r fig.width=5, fig.height=6}
sub_inds <- sample(n_train, floor(n_train)/2)
res <- cv.glmnet(x = feature_train[sub_inds, ], y = train_resp[sub_inds, voxel], alpha = 1, type.measure="mse")
l <- res$lambda.min
beta_vec <- coef(res, s = l)
plot(beta_vec)

image(get_filter(beta_vec))
```



It is sort of stable in that the filters look the same, but those two very large parameters in the first model are now gone. We also tried elastic net, which has the objective $||y - X\beta||^2 + \alpha \lambda ||\beta||_1 + (1-\alpha) ||\beta||^2$.


```{r fig.width=5, fig.height=6}
sub_inds <- sample(n_train, floor(n_train)/2)
res <- cv.glmnet(x = feature_train[sub_inds, ], y = train_resp[sub_inds, voxel], alpha = 0.5, type.measure="mse")
l <- res$lambda.min
beta_vec <- coef(res, s = l)
plot(beta_vec)

image(get_filter(beta_vec))
```

