Exercise 4
========================================================
Nora Brackbill and Charles Zheng

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, warning=FALSE)
```

## Load the data

```{r, cache=FALSE}
library('car')
library('pdist')
load('ex4.RData')
```

## Visualize the filters

```{r fig.width=5, fig.height=6}
rematwav <- function(ind, wav = wav.pyr) {
  wav <- matrix(Re(wav[, ind]), 128, 128)
}
old.par <- par()
layout(matrix(1:42, 7, 6))
par(mar = c(0,0,0,0))
for (i in which(vertical_features)) {
  image(rematwav(i, wav.pyr42), axes=FALSE)  
}
for (i in which(horizontal_features)) {
  image(rematwav(i, wav.pyr42), axes=FALSE)  
}
```

## Get the p-values

We fit a linear model to each voxel from the 42 features, and calculated the F-statistic for the null hypothesis that 

$\sum$ horizontal features - $\sum$ vertical features = 0.


```{r fig.width=5, fig.height=6}
contrast_vec <- c(0, -1 * vertical_features + 
                   1 * horizontal_features)
nvoxels <- dim(train_resp)[2]
pvs <- numeric(nvoxels)
for (vox in 1:nvoxels) {
  res <- lm(train_resp[, vox] ~ X)
  res2 <- linearHypothesis(res, t(contrast_vec))
  pvs[vox] <- res2$'Pr(>F)'[2]
}
plot(1:nvoxels/nvoxels, sort(pvs), main="P-P Plot", xlab="Uniform", ylab="Calculated")
lines(0:1,0:1)
```

## Plot the p-values aross the brain slice

```{r fig.width=6, fig.height=6}
a=matrix(1,60,60)
for (i in 1:nvoxels){ 
  a[vl[i,1],vl[i,2]] <- pvs[i] 
}
image(a[12:55,9:51], axes=FALSE)
```

## How many are significant at level 0.1, and where are they?

```{r fig.width=7, fig.height=6}
sum(pvs < .1)

plot(vl[,1], vl[,2], col='grey')
points(vl[pvs < .1, ], col='red')
```

## Bonferroni correction

What is the p-value threshold for the Bonferroni method at FWE=0.3? 

```{r}
p_bon <- 0.3/nvoxels
print(p_bon)
```

How many are significant?

```{r}
sig_voxels_Bon <- pvs < p_bon
sum(sig_voxels_Bon)
```

Plot:

```{r fig.width=7, fig.height=6}
plot(vl[,1], vl[,2], col='grey')
points(vl[pvs < .1, ], col='red')
points(vl[sig_voxels_Bon, ], col='black', pch='|')
legend("bottomright",c("No Control", "Bonferonni"), col=c('red', 'black'), pch=c('o','|'))
```

## BH procedure

The threshold p-value for BH is the highest p-value that was below the BH cutoff $p_i = i \frac{\alpha}{n}$. We used $\alpha$=0.3.

```{r fig.width=5, fig.height=6}
alpha <- 0.3;
for (vox in 1:nvoxels){
  if (sort(pvs)[vox] > alpha*vox/nvoxels){
    break
  }
}
pthres<-alpha*vox/nvoxels
print(pthres)
plot(1:100/nvoxels, sort(pvs)[1:100], main="P-P Plot", xlab="Uniform", ylab="Calculated")
lines(c(0,100/nvoxels),c(0,alpha*100/nvoxels),col='red')
legend("bottomright", 'BH cutoff line',lty=1, col='red')
```

How many are significant?

```{r}
fdr_vox <- pvs <= pthres
sum(fdr_vox)
```

Plot:

```{r fig.width=7, fig.height=6}
plot(vl, col='grey', pch=20)
points(vl[pvs<0.1,], col='red', pch=20) 
points(vl[order(pvs)[1:vox],], col='black', pch='o')
points(vl[sig_voxels_Bon,],col='black', pch='|')
legend("bottomright",c("No control", "B-H FDR", "Bonferonni"), col=c('red', 'black', 'black'), pch=c('o','o','|'))

```

## FWE by permutation

We randomized the images by reordering the rows of X, the design matrix.

```{r fig.width=7, fig.height=6, eval=FALSE,}
nimages=dim(X)[1]
n_repeats=50
P_min_null=numeric(n_repeats)
 for (i in 1:n_repeats){
  X_random=X[sample(1:nimages),]
  P_null = numeric(nvoxels)
  for (j in 1:nvoxels){
    res <- lm(train_resp[,j] ~ X_random)
    res2 <- linearHypothesis(res, t(contrast_vec))
    P_null[j]= res2$'Pr(>F)'[2]
  }
  P_min_null[i]=min(P_null)
}
hist(P_min_null,breaks=20, xlim=c(0,pthres+0.002))
lines(c(p_bon, p_bon),c(0,50), col='red')
lines(c(pthres, pthres),c(0,50), col='blue')
legend("topright", c('Bonferonni','BH FDR'),lty=1, col=c('red','blue'))
save(file='p_min.RData', P_min_null)
```

```{r fig.width=7, fig.height=6, echo=FALSE}
nimages=dim(X)[1]
n_repeats=50
load('p_min.RData')
hist(P_min_null, breaks=20, xlim=c(0,pthres+0.002))
lines(c(p_bon, p_bon),c(0,50), col='red', lwd=2)
lines(c(pthres, pthres),c(0,50), col='blue', lwd=2)
legend("topright", c('Bonferonni','BH FDR'),lty=1, col=c('red','blue'))
```
